### 2021-09-03 paper/paper.tex
update

@@

\begin{figure}[h]
    \centering
    \subfigure{
        \label{Fig.sub.1}
        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_n.png}}
    \subfigure{
        \label{Fig.sub.2}
        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_n.png}}
    \subfigure{
        \label{Fig.sub.3}
        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_n.png}}
    \caption{Loss value, parameter matrix error, accuracy versus number of data points($d=64, \sigma=1.0, c=10$)}
    \label{Fig.1}

    \subfigure{
        \label{Fig.sub.1}
        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_d.png}}
    \subfigure{
        \label{Fig.sub.2}
        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_d.png}}
    \subfigure{
        \label{Fig.sub.3}
        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_d.png}}
    \caption{Loss value, parameter matrix error, accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, c=10$)}
    \label{Fig.2}

    \subfigure{
        \label{Fig.sub.1}
        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_sigma.png}}
    \subfigure{
        \label{Fig.sub.2}
        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_sigma.png}}
    \subfigure{
        \label{Fig.sub.3}
        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_sigma.png}}
    \caption{Loss value, parameter matrix error, accuracy versus randomness($n=100, d=64, c=10$)}
    \label{Fig.3}

    \subfigure{
        \label{Fig.sub.1}
        \includegraphics[width=0.3\textwidth]{fig/images/loss_vs_class.png}}
    \subfigure{
        \label{Fig.sub.2}
        \includegraphics[width=0.3\textwidth]{fig/images/error_vs_class.png}}
    \subfigure{
        \label{Fig.sub.3}
        \includegraphics[width=0.3\textwidth]{fig/images/accuracy_vs_class.png}}
    \caption{Loss value, parameter matrix error, accuracy versus number of classes($n=100, d=64, \sigma=1.0$)}
    \label{Fig.4}

@@

@@

\subsection{Pseudo-synthetic data}
In a pseudo-synthetic dataset, we take a non-synthetic dataset and modify it.
\fixme{describe your procedure for generating pseudo-synthetic data and all the experiments that you plan to run}
\subsubsection{Constructing Pseudo-synthetic datasets}
\label{sec:pseu-syn}
In order to compare the performance between classic cross entropy loss function and cover tree loss function, we need datasets which the classes have clear similarities.
Besides, we would like to construct pseudo-synthetic datasets which we can control the similarities.
The idea is we can generate the new classes from the original classes of datasets.
This impilies only the labels are synthetic and the features are real.
We get the similarities of new classes from probability distribution and control the complexity of similarities by changing probability distribution.

>>>>

HSM:
\begin{equation}
    \label{eq:xentropy}
    \ell(W;(\x,y)) = - \log \prod_{k\in P_y}\frac {\exp(-\trans\w_k \x)}{\sum_{j=1}^c \exp(-\trans \w_j \x)}
\end{equation}
where $P_y$ is path from root to node of Huffman Tree

@@

\begin{figure}[h]
    \centering
    \subfigure{
        \label{Fig.sub.1}
        \includegraphics[width=0.3\textwidth]{fig/log_images/loss_vs_n.png}}
    \subfigure{
        \label{Fig.sub.2}
        \includegraphics[width=0.3\textwidth]{fig/log_images/error_vs_n.png}}
    \subfigure{
        \label{Fig.sub.3}
        \includegraphics[width=0.3\textwidth]{fig/log_images/accuracy_vs_n.png}}
    \caption{Loss value, parameter matrix error, accuracy versus number of data points($d=64, \sigma=1.0, c=10$)}
    \label{Fig.1}

    \subfigure{
        \label{Fig.sub.1}
        \includegraphics[width=0.3\textwidth]{fig/log_images/loss_vs_d.png}}
    \subfigure{
        \label{Fig.sub.2}
        \includegraphics[width=0.3\textwidth]{fig/log_images/error_vs_d.png}}
    \subfigure{
        \label{Fig.sub.3}
        \includegraphics[width=0.3\textwidth]{fig/log_images/accuracy_vs_d.png}}
    \caption{Loss value, parameter matrix error, accuracy versus dimension of parameter matrix($n=100, \sigma=1.0, c=10$)}
    \label{Fig.2}

    \subfigure{
        \label{Fig.sub.1}
        \includegraphics[width=0.3\textwidth]{fig/log_images/loss_vs_sigma.png}}
    \subfigure{
        \label{Fig.sub.2}
        \includegraphics[width=0.3\textwidth]{fig/log_images/error_vs_sigma.png}}
    \subfigure{
        \label{Fig.sub.3}
        \includegraphics[width=0.3\textwidth]{fig/log_images/accuracy_vs_sigma.png}}
    \caption{Loss value, parameter matrix error, accuracy versus randomness($n=100, d=64, c=10$)}
    \label{Fig.3}

    \subfigure{
        \label{Fig.sub.1}
        \includegraphics[width=0.3\textwidth]{fig/log_images/loss_vs_class.png}}
    \subfigure{
        \label{Fig.sub.2}
        \includegraphics[width=0.3\textwidth]{fig/log_images/error_vs_class.png}}
    \subfigure{
        \label{Fig.sub.3}
        \includegraphics[width=0.3\textwidth]{fig/log_images/accuracy_vs_class.png}}
    \caption{Loss value, parameter matrix error, accuracy versus number of classes($n=100, d=64, \sigma=1.0$)}
    \label{Fig.4}

@@

\subsubsection{Analysis of Synthetic Experiment results}

From \ref{Fig.1}, as number of data points increases loss value and parameter matrix error decrease while accuracy increases. 
We compare the performance of cover tree loss, softmax cross entropy loss and simloss, it is clear that cover tree loss converges faster than the other two loss functions.
Besides, cover tree loss achieves lower loss value and parameter matrix error over number of data points.

As shown in \ref{Fig.2}, loss value decreases and accuracy increases over dimension. 
Similar to \ref{Fig.1}, cover tree loss converges faster and achieve lower loss value.
We take the line of parameter matrix error of cover tree loss as a benchmark and draw the difference of parameter matrix error between cover tree loss and the other two loss functions.
The middle sub-figure indicates that cover tree loss has lower parameter matrix error with dimension than cross entropy and simloss.

According to \ref{Fig.3}, if we increase the randomness and fix the other parameters, loss value increases and accuracy decreases.
Cover tree loss performs similarly with cross entropy loss and simloss in terms of loss value and accuracy.
The middle sub-figure implies that parameter matrix error of cover tree loss decreases even though the randomness increases.

\ref{Fig.4} indicates that, as number of classes increases, the loss value and parameter matrix error also increases and accuracy certainly decrease.
From middle sub-figure, the parameter matrix error of cover tree loss is lower than the other two loss functions.
The right sub-figure shows that the accuracy of cover tree loss decreases slower and can keep higher value than the other two loss functions.

@@

\subsection{Pseudo-synthetic data}
In a pseudo-synthetic dataset, we take a non-synthetic dataset and modify it.
\fixme{describe your procedure for generating pseudo-synthetic data and all the experiments that you plan to run}
\subsubsection{Constructing Pseudo-synthetic datasets}
\label{sec:pseu-syn}
In order to compare the performance between classic cross entropy loss function and cover tree loss function, we need datasets which the classes have clear similarities.
Besides, we would like to construct pseudo-synthetic datasets which we can control the similarities.
The idea is we can generate the new classes from the original classes of datasets.
This implies that only the labels are synthetic and the features are real.
We get the similarities of new classes from probability distribution and control the complexity of similarities by changing probability distribution.
